---
title: "Labwork3"
author: "Andrew Chen"
date: "2/7/2019"
output: html_document
---

```{r}
library(dplyr)
library(magrittr)
library(ggplot2)
library(ggfortify)
```

```{r}
exam = read.csv('118.5 Woodcock Data Entry_4.2.19_RJ.csv', stringsAsFactors = F)
exam$correct[which(is.na(exam$correct))] = 0
```

```{r}
incorrect = exam[exam$correct == 0 & exam$response != "", ]
exam[exam$response == "5.3", "correct"] = 1
exam["3634", "correct"] = 1
```

```{r}
id = c()
standard = c()
score = c()
class = c()
gender = c()
order = c()
batch = c()
for(i in 1:66) {
  x = exam$id[57*(i - 1) + 1]
  standard[i] = exam$standard[57*(i - 1) + 1]
  class[i] = exam$class[57*(i - 1) + 1]
  gender[i] = exam$gender[57*(i - 1) + 1]
  order[i] = exam$order[57*(i - 1) + 1]
  batch[i] = exam$batch[57*(i - 1) + 1]
  id[i] = x
  score[i] = sum(exam[exam$id == x, ]$correct)
}
```

##Exam Before Exclusions
```{r}
Exam = data.frame(id = id, standard = standard, class = class, gender = gender, order = order, batch = batch, score = score)

summary(score)
hist(score, breaks = 20)
```

###Summary Statistics of Data by Groups
```{r}
gen_count = Exam %>% count(gender)
class_count = Exam %>% count(class)
standard_count = Exam %>% count(standard)
batch_count = Exam %>% count(batch)
order_count = Exam %>% count(order)
```

```{r}
#Average Score grouped by Gender
Exam %>% group_by(gender) %>% summarise(mean = mean(score)) %>% mutate(freq = gen_count$n) %>% arrange(desc(mean))

#Average Score grouped by Class
Exam %>% group_by(class) %>% summarise(mean = mean(score)) %>% mutate(freq = class_count$n) %>% arrange(desc(mean))

#Average Score grouped by Standard
Exam %>% group_by(standard) %>% summarise(mean = mean(score)) %>% mutate(freq = standard_count$n) %>% arrange(desc(mean))

#Average Score grouped by Batch
Exam %>% group_by(batch) %>% summarise(mean = mean(score)) %>% mutate(freq = batch_count$n) %>% arrange(desc(mean))

#Average Score grouped by Order
Exam %>% group_by(order) %>% summarise(mean = mean(score)) %>% mutate(freq = order_count$n) %>% arrange(desc(mean))
```

###Relationship Between Gender and Score
```{r}
t.test(Exam[Exam$gender == "f",]$score, Exam[Exam$gender == "m",]$score)
```

###Relationship Between Standard and Score
```{r}
anova(lm(score ~ standard, data = Exam))
```

###Relationship Between Batch and Score
```{r}
anova(lm(score ~ batch, data = Exam))
```

###Relationship Between Order and Score
```{r}
t.test(Exam[Exam$order == "kinship first",]$score, Exam[Exam$order == "number first",]$score)
```

###Relationship Between Class and Score
```{r}
anova(lm(score ~ class, data = Exam[-which(Exam$standard == 7),]))
```

##Number Similarity Data: Before Exclusions
```{r}
number = read.csv('118.5 Number Similarity Data Entry_2.19.19_RJ.csv', stringsAsFactors = F)
number = number[-which(number$item1 == "reflection" | number$form == "reflection"),]
```

####Unifying Data
```{r}
id = c()
standard = c()
class = c()
gender = c()
order = c()
version = c()

for (i in 1:66) {
  id[i] = number$id[98 * (i - 1) + 1]
  standard[i] = number$standard[98 * (i-1) + 1]
  class[i] = number$class[98*(i-1)+1]
  gender[i] = number$gender[98*(i-1)+1]
  order[i] = number$order[98*(i-1)+1]
  version[i] =  ifelse(grepl('versa', number$version[98*(i-1)+1]) == TRUE, 'versa', 'vice')
}

Number = data.frame(id = id, standard = standard, class = class, gender = gender, order = order, version = version)
```

###Isolating Attention Checks
```{r}
attention = number[number$item1 == number$item2,]
number = number[-which(number$item1 == number$item2),]
```

###Adding Attention Check Scores
```{r}
num1att = c()
num2att = c()
for (i in 1:66) {
  num1att[i] = sum(attention[(8*(i-1)+1):(8*(i-1)+4),]$response == 5)
  num2att[i] = sum(attention[(8*(i-1)+5):(8*i),]$response == 5)
}

Number = cbind(Number, num1att, num2att)
```

###Creating Matrix of Numbers
```{r}
numbers = c(5,14,16,9,29,8,11,20,18,21)
numbers2 = c(7,25,12,17,28,6,13,4,27,10)
num_mat = matrix(0,10,10)
num_mat2 = matrix(0,10,10)
for (i in 1:10) {
  num_mat[,i] = numbers
  numbers = numbers[c(2:10, 1)]
}

for (j in 1:10) {
  num_mat2[,j] = numbers2
  numbers2 = numbers2[c(2:10,1)]
}

num_mat = cbind(num_mat, num_mat2)
colnames(num_mat) = rep(NULL, 20)
```

###Adding columns of compared number pairs
```{r}
cols = c()
cols2 = c()
total = 0

for (i in 1:9) {
  x = 9 - (i - 1)
  for (j in 1:x) {
    num1 = num_mat[j, 1]
    num2 = num_mat[j, i+1]
    n1 = num_mat2[j, 1]
    n2 = num_mat2[j, i+1]
    nums = paste0(num1, '/', num2)
    ns = paste0(n1, '/', n2)
    cols[total + j] = nums
    cols2[total + j] = ns
  }
  total = total + x
}
```

```{r}
for (i in 1:90) {
  ratings = c()
  for (j in 1:66) {
    ratings[j] = number[90*(j-1)+i,"response"]
    ratings = as.numeric(ratings)
  }
  Number = cbind(Number, ratings)
}
```

```{r}
for (i in 1:45) {
  colnames(Number)[8+i] = cols[i]
  colnames(Number)[53+i] = cols2[i]
}
```

###Fixing Dates & Responses
```{r}
number[number$dot == "17-Jan", "dot"] = '19/1/17'
number[number$dot == "10/1/10", "dot"] = '19/1/10'
number[number$response == 44 & !is.na(number$response), "response"] = 4
```

###Counting Correct Attention Checks
```{r}
a = rep(0:4, each = 5)
b = rep(0:4, 5)
att_counts = c()
categories = c()

for (i in 1:25) {
  att_counts[i] = nrow(Number[Number$num1att == a[i] & Number$num2att == b[i], ])
  categories[i] = paste0(a[i], '/', b[i])
}

names(att_counts) = categories
att_counts
```

###Adding Exam Scores to Number Data
```{r}
scores = rep(NA, nrow(Number))
for (i in 1:nrow(Number)) {
  index = which(grepl(Exam$id[i], Number$id) == T)
  scores[index] = Exam$score[i]
}

Number = cbind(Number, scores)
```

###Counting NAs
```{r}
NAs = c()
for(i in 1:66) {
  NAs[i] = sum(is.na(Number[i,]))
}
Number = cbind(Number, NAs)
table(Number$NAs)
```

###Regression of Response with Standard and Version
```{r}
number$response = as.numeric(number$response)
vers = c()
for (i in 1:nrow(number)) {
  vers[i] = ifelse(grepl('vice', number[i, "version"]), 'vice', 'versa')
}
number = cbind(number, vers)
mod = lm(response ~ vers + standard, data = number)
summary(mod)
```

###Boxplot and Summary of Vice vs. Versa
```{r}
boxplot(number$response ~ number$vers)
summary(number[number$vers == "vice", "response"])
summary(number[number$vers == "versa", "response"])
```

##After Exclusions

###Making Exclusions in Number Data
```{r}
Number$id = as.character(Number$id)
Exam$id = as.character(Exam$id)
Number = Number[(Number$NAs < 5), ]
Number = Number[(Number$num1att > 2 & Number$num2att > 2), ]
rownames(Number) = 1:nrow(Number)
```

###Corresponding Exclusions in Exam Data
```{r}
indices = c()
for (i in 1:nrow(Number)) {
  indices[i] = which(Exam$id == as.character(Number$id[i]))
}

Exam = Exam[indices, ]
rownames(Exam) = 1:nrow(Exam)
```

###Corresponding Exclusions in Original Number Data
```{r}
number$id = as.character(number$id)
indices = c()
for (i in 1:nrow(Number)) {
  indices = c(indices, which(number$id == as.character(Number$id[i])))
}

number = number[indices, ]
rownames(number) = 1:nrow(number)
```

###Regression of Response with Standard and Version - Post Exclusion
```{r}
mod = lm(response ~ vers + standard, data = number)
summary(mod)
```

###Boxplot and Summary of Vice vs. Versa - Post Exclusion
```{r}
boxplot(number$response ~ number$vers)
summary(number[number$vers == "vice", "response"])
summary(number[number$vers == "versa", "response"])
```

##Exam Data Analysis - Post Exclusion

###Summary Statistics of Data by Groups
```{r}
gen_count = Exam %>% count(gender)
class_count = Exam %>% count(class)
standard_count = Exam %>% count(standard)
batch_count = Exam %>% count(batch)
order_count = Exam %>% count(order)
```

```{r}
Exam %>% group_by(gender) %>% summarise(mean = mean(score)) %>% mutate(freq = gen_count$n) %>% arrange(desc(mean))

Exam %>% group_by(class) %>% summarise(mean = mean(score)) %>% mutate(freq = class_count$n) %>% arrange(desc(mean))

Exam %>% group_by(standard) %>% summarise(mean = mean(score)) %>% mutate(freq = standard_count$n) %>% arrange(desc(mean))

Exam %>% group_by(batch) %>% summarise(mean = mean(score)) %>% mutate(freq = batch_count$n) %>% arrange(desc(mean))

Exam %>% group_by(order) %>% summarise(mean = mean(score)) %>% mutate(freq = order_count$n) %>% arrange(desc(mean))
```

###Summary of people who got vice/versa, by standard
```{r}
Number %>% group_by(standard) %>% count(version)
```

###Relationship Between Gender and Score
```{r}
t.test(Exam[Exam$gender == "f",]$score, Exam[Exam$gender == "m",]$score)
```

###Relationship Between Standard and Score
```{r}
anova(lm(score ~ standard, data = Exam))
```

###Relationship Between Batch and Score
```{r}
anova(lm(score ~ batch, data = Exam))
```

###Relationship Between Order and Score
```{r}
t.test(Exam[Exam$order == "kinship first",]$score, Exam[Exam$order == "number first",]$score)
```

###Relationship Between Class and Score
```{r}
anova(lm(score ~ class, data = Exam[-which(Exam$standard == 7),]))
```

###Pairwise Boxplots
```{r}
par(mfrow = c(3,4))
for(i in 1:90) {
  nums = as.numeric(unlist(strsplit(colnames(Number)[8+i], split = '/')))
  versa = paste0(nums[2], "/", nums[1])
  boxplot(Number[, 8+i] ~ Number$version, main = colnames(Number)[8+i], names = c(versa, colnames(Number[8+i])))
}
```

###t-tests and boxplots for pairs of numbers with discrepancies in vice/versa judgments
```{r}
t.test(Number[Number$version == "vice", "16/9"], Number[Number$version == "versa", "16/9"])
t.test(Number[Number$version == "vice", "5/20"], Number[Number$version == "versa", "5/20"])
t.test(Number[Number$version == "vice", "8/21"], Number[Number$version == "versa", "8/21"])
t.test(Number[Number$version == "vice", "5/21"], Number[Number$version == "versa", "5/21"])

par(mfrow = c(3,2))
boxplot(Number[Number$standard == 3 | Number$standard == 4, "16/9"] ~ Number[Number$standard == 3 | Number$standard == 4,]$version, main = "16/9, Standard 3 & 4")

boxplot(Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7 , "16/9"] ~ Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7,]$version, main = "16/9, Standard 5-7")

boxplot(Number[Number$standard == 3 | Number$standard == 4, "5/20"] ~ Number[Number$standard == 3 | Number$standard == 4,]$version, main = "5/20, Standard 3 & 4")

boxplot(Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7 , "5/20"] ~ Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7,]$version, main = "5/20, Standard 5-7")

boxplot(Number[Number$standard == 3 | Number$standard == 4, "8/21"] ~ Number[Number$standard == 3 | Number$standard == 4,]$version, main = "8/21, Standard 3 & 4")

boxplot(Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7 , "8/21"] ~ Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7,]$version, main = "8/21, Standard 5-7")

boxplot(Number[Number$standard == 3 | Number$standard == 4, "5/21"] ~ Number[Number$standard == 3 | Number$standard == 4,]$version, main = "5/21, Standard 3 & 4")

boxplot(Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7 , "5/21"] ~ Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7,]$version, main = "5/21, Standard 5-7")
```

##MDS Plot: Grand Average
```{r}
avg_comp = c()
for (i in 1:90) {
  avg_comp[i] = mean(Number[,8+i],na.rm = T)
}

names(avg_comp) = colnames(Number)[9:98]

sim_mat1 = matrix(0,10,10)
sim_mat2 = matrix(0,10,10)
rownames(sim_mat1) = as.character(numbers)
colnames(sim_mat1) = as.character(numbers)
rownames(sim_mat2) = as.character(numbers2)
colnames(sim_mat2) = as.character(numbers2)

for (j in 1:10) {
  sim_mat1[j, j] = 100
  sim_mat2[j, j] = 100
}

for (i in 1:45) {
  nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
  nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
  sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
  sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
  sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
  sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
}

```

```{r}
mds_avg1 = cmdscale(100 - sim_mat1)
mds_avg2 = cmdscale(100 - sim_mat2)
plot(mds_avg1,cex = .1)
abline(v=0,h=0)
text(mds_avg1[,1], mds_avg1[,2], labels = numbers)
plot(mds_avg2,cex = .1)
abline(v=0,h=0)
text(mds_avg2[,1], mds_avg2[,2], labels = numbers2)
```

###MDS Plots by Standard
```{r}
par(mfrow = c(2,2))
for (g in 3:7) {
  avg_comp = c()
  for (i in 1:90) {
    avg_comp[i] = mean(Number[Number$standard == g , 8+i],na.rm = T)
  }

  names(avg_comp) = colnames(Number)[9:98]

  sim_mat1 = matrix(0,10,10)
  sim_mat2 = matrix(0,10,10)
  rownames(sim_mat1) = as.character(numbers)
  colnames(sim_mat1) = as.character(numbers)
  rownames(sim_mat2) = as.character(numbers2)
  colnames(sim_mat2) = as.character(numbers2)

  for (j in 1:10) {
    sim_mat1[j, j] = 100
    sim_mat2[j, j] = 100
  }

  for (i in 1:45) {
    nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
    nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
    sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
    sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
    sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
    sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
  }

  mds_avg1 = cmdscale(100 - sim_mat1)
  mds_avg2 = cmdscale(100 - sim_mat2)
  plot(mds_avg1,cex = .1, main = paste("MDS Plot 1, Standard", g))
  abline(v=0,h=0)
  text(mds_avg1[,1], mds_avg1[,2], labels = numbers)
  plot(mds_avg2,cex = .1, main = paste("MDS Plot 2, Standard", g))
  abline(v=0,h=0)
  text(mds_avg2[,1], mds_avg2[,2], labels = numbers2)
}
```

###MDS Plots for Standards 3/4 and 6/7
```{r, eval = F}
par(mfrow = c(2,2))
for (d in 1:2) {
  avg_comp = c()
  for (i in 1:90) {
    avg_comp[i] = mean(Number[Number$standard == (3*d) | Number$standard == (3*d+1) , 8+i], na.rm = T)
  }

  names(avg_comp) = colnames(Number)[9:98]

  sim_mat1 = matrix(0,10,10)
  sim_mat2 = matrix(0,10,10)
  rownames(sim_mat1) = as.character(numbers)
  colnames(sim_mat1) = as.character(numbers)
  rownames(sim_mat2) = as.character(numbers2)
  colnames(sim_mat2) = as.character(numbers2)
  
  for (j in 1:10) {
    sim_mat1[j, j] = 100
    sim_mat2[j, j] = 100
  }

  for (i in 1:45) {
    nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
    nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
    sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
    sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
    sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
    sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
  }
  
  mds_avg1 = cmdscale(100 - sim_mat1)
  mds_avg2 = cmdscale(100 - sim_mat2)
  plot(mds_avg1,cex = .1, main = paste("MDS Plot 1, Standards", (3*d), "&", (3*d+1)))
  abline(v=0,h=0)
  text(mds_avg1[,1], mds_avg1[,2], labels = numbers)
  plot(mds_avg2,cex = .1, main = paste("MDS Plot 2, Standards", (3*d), "&", (3*d+1)))
  abline(v=0,h=0)
  text(mds_avg2[,1], mds_avg2[,2], labels = numbers2)
}
```


###MDS ggplot, Standards 3 & 4
```{r}
avg_comp = c()
  for (i in 1:90) {
    avg_comp[i] = mean(Number[Number$standard == 3 | Number$standard == 4 , 8+i], na.rm = T)
  }

  names(avg_comp) = colnames(Number)[9:98]

  sim_mat1 = matrix(0,10,10)
  sim_mat2 = matrix(0,10,10)
  rownames(sim_mat1) = as.character(numbers)
  colnames(sim_mat1) = as.character(numbers)
  rownames(sim_mat2) = as.character(numbers2)
  colnames(sim_mat2) = as.character(numbers2)
  
  for (j in 1:10) {
    sim_mat1[j, j] = 100
    sim_mat2[j, j] = 100
  }

  for (i in 1:45) {
    nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
    nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
    sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
    sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
    sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
    sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
  }

  autoplot(cmdscale(100-sim_mat1, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 1, Standards 3 & 4, n = 19")+ theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
  
  autoplot(cmdscale(100-sim_mat2, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 2, Standards 3 & 4, n = 19")+ theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
```

###MDS ggplot Standards 5-7
```{r}
avg_comp = c()
for (i in 1:90) {
  avg_comp[i] = mean(Number[Number$standard == 5 | Number$standard == 6 | Number$standard == 7 , 8+i], na.rm = T)  
}

  names(avg_comp) = colnames(Number)[9:98]

  sim_mat1 = matrix(0,10,10)
  sim_mat2 = matrix(0,10,10)
  rownames(sim_mat1) = as.character(numbers)
  colnames(sim_mat1) = as.character(numbers)
  rownames(sim_mat2) = as.character(numbers2)
  colnames(sim_mat2) = as.character(numbers2)
  
  for (j in 1:10) {
    sim_mat1[j, j] = 100
    sim_mat2[j, j] = 100
  }

  for (i in 1:45) {
    nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
    nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
    sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
    sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
    sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
    sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
  }
  
  autoplot(cmdscale(100-sim_mat1, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 1, Standards 5-7, n = 29") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
  
  autoplot(cmdscale(100-sim_mat2, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 2, Standards 5-7, n = 29") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
```

###MDS plots for top and bottom quartile
```{r}
order_score = arrange(Number, scores)
top_quartile = Number[Number$scores >= 34, ]
bottom_quartile = Number[Number$scores < 28.75, ]
```

```{r}
avg_comp = c()
for (i in 1:90) {
  avg_comp[i] = mean(top_quartile[, 8+i], na.rm = T)  
}

  names(avg_comp) = colnames(Number)[9:98]

  sim_mat1 = matrix(0,10,10)
  sim_mat2 = matrix(0,10,10)
  rownames(sim_mat1) = as.character(numbers)
  colnames(sim_mat1) = as.character(numbers)
  rownames(sim_mat2) = as.character(numbers2)
  colnames(sim_mat2) = as.character(numbers2)
  
  for (j in 1:10) {
    sim_mat1[j, j] = 100
    sim_mat2[j, j] = 100
  }

  for (i in 1:45) {
    nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
    nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
    sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
    sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
    sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
    sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
  }
  
  autoplot(cmdscale(100-sim_mat1, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 1, Top Quartile, n = 13") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
  
  autoplot(cmdscale(100-sim_mat2, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 2, Top Quartile, n = 13") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
```

```{r}
avg_comp = c()
for (i in 1:90) {
  avg_comp[i] = mean(bottom_quartile[, 8+i], na.rm = T)  
}

  names(avg_comp) = colnames(Number)[9:98]

  sim_mat1 = matrix(0,10,10)
  sim_mat2 = matrix(0,10,10)
  rownames(sim_mat1) = as.character(numbers)
  colnames(sim_mat1) = as.character(numbers)
  rownames(sim_mat2) = as.character(numbers2)
  colnames(sim_mat2) = as.character(numbers2)
  
  for (j in 1:10) {
    sim_mat1[j, j] = 100
    sim_mat2[j, j] = 100
  }

  for (i in 1:45) {
    nums1 = unlist(strsplit(names(avg_comp)[i], split = "/"))
    nums2 = unlist(strsplit(names(avg_comp)[45+i], split = "/"))
    sim_mat1[nums1[1], nums1[2]] = avg_comp[i] * 20
    sim_mat1[nums1[2], nums1[1]] = avg_comp[i] * 20
    sim_mat2[nums2[1], nums2[2]] = avg_comp[45+i] * 20
    sim_mat2[nums2[2], nums2[1]] = avg_comp[45+i] * 20
  }
  
  autoplot(cmdscale(100-sim_mat1, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 1, Bottom Quartile, n = 12") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
  
  autoplot(cmdscale(100-sim_mat2, eig = T), label = T, label.size = 5, size = 0) + geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + xlab("") + ylab("") + ggtitle("MDS Plot 2, Bottom Quartile, n = 12") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())
```

###Summary Stats for Top and Bottom Quartile
```{r}
bottom_quartile %>% count(gender)
bottom_quartile %>% count(class)
bottom_quartile %>% count(standard)
bottom_quartile %>% count(order)
```

```{r}
top_quartile %>% count(gender)
top_quartile %>% count(class)
top_quartile %>% count(standard)
top_quartile %>% count(order)
```

```{r}
boxplot(top_quartile$scores)
boxplot(bottom_quartile$scores)
```